Modalities for Location Virtualization

### 2022-09-20 examples.tex
update example's work division
another asm snippet

\section{Experiment}
\label{sec:experiment}
\mytodo{Ismail's Part}

>>>>

\section{Experiment}
\label{sec:experiment}
\mytodo{Mechanization is Ismail's Part -- Discussing and putting in here is Colin's}

To both validate and demonstrate the value of the modal approach to reasoning about virtual memory management, we study several distillations of real concerns of virtual memory managers.
Recall from Section \ref{sec:logic} that virtual points-to assertions work just like regular points-to assertions, by design.

\subsection{Identity Mappings}
\todo[inline]{need to describe this}

\subsection{Mapping a New Page}
One of the key tasks of a page fault handler in a general-purpose OS kernel is to map new pages into an address space by writing into an existing page table.
\todo[inline]{Ismail, see notes about intermediate assertions on the Notion page}
\begin{figure}
\begin{lstlisting}
;; Assume the faulting address f is in r12,
;; a callee-save register, and f with the 
;; lower 12 bits zeroed out (so, the virtual
;; page containing f) is in r13 (also callee-save)

;; Ensure there's a place to put the L1 mapping
mov %rdi, r13
call ensure_L1_page
;; Returns the virtual address of the L1 entry in rax
mov %r14, %rax ;; Save that before another call
call alloc_phys_page_or_panic
;; Calculate new PTE by setting the low-order bits
;; of the physical page
add %rax, 3
;; update the page table entry, mapping the page
mov (%rcx), %rax
;; memset the newly-mapped page
mov %rdi, r13
mov %rsi, 0
mov %rdx, 4096
call memset
;; The newly mapped page is full of 0s
\end{lstlisting}
\caption{Distilled code for mapping a new page}
\label{fig:mapping_code}
\todo[inline]{this is terribly ugly, should switch to minted}
\end{figure}

\todo[inline]{emphasize the write to the L1 page table is validated by the fact that the identity mapping exists}

\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.

\subsection{Change of Address Space}
A critical piece of \emph{trusted} code in verified OS kernels is the assembly code to change the current address space; current verified OS kernels currently lack effective ways to specify and reason about this low-level operation, for resaons outlined in Section \ref{sec:relwork}.

\todo[inline]{probably not much more than just the cr3 update, but could be extended to a full context switch since the instruction pointer isn't updated in a swtch}

\begin{lstlisting}
;; Assume the save-space is in rdi,
;; load-space in rsi
;; No need to save/restore caller-save regs
;; Save yielding context
mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15
mov 56[%rdi], %cr3
;; Restore target context
mov %rbx, 0[%rsi] 
;; This switches to a new stack
;; This stack may not be mapped in the
;; current address space!
mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]
;; Switch to the new address space
mov %cr3, 56[%rsi]
\end{lstlisting}
\todo[inline]{technically we weren't planning to prove reads of cr3...}
\todo[inline]{need to figure out the right pre/post condition to highlight the change in address space, beyond the vpoints-to of the two structures}
